Pillar 2 - Topic Modeling

### 2019-04-12 Pillar 2 - Topic Modeling.Rmd
use my_control instead of my_control_fast
minor change: control seed change number

  nstart = 10,
  seed   = 1 : 10,
  best   = TRUE,

@@

```
###Training Models
We train the LDA for different numbers of topics (5 to 250 by 5), we save the resulting 50 models under `topic_model`, along with the DTM used to build the model, the corpus of origin (overview or manuals), the word and topic distributions results from that model, it's evaluation measures, and vectors of words and topics that allow us humans to get a feel of the model, along with some key words.
```{r LDA fit, cache = TRUE, eval = TRUE}
topic_numbers <- seq(from = 5, to = 15, by = 5)

@@

  ) %>%
  mutate(Origin     = rep(c("catalogues", "manuals"), 3),         # should be 50
         `Topic ID` = paste(Origin, n_topic, sep = "_"),

@@

         #Fit Model
         Model  = pmap(.l = list(n_topic, DTM), .f = my_LDA, control = my_control_fast), #my_control

>>>>

  nstart = 20,
  seed   = 1 : 20,
  best   = TRUE,

@@

```
###Training Models
We train the LDA for different numbers of topics (5 to 250 by 5), we save the resulting 50 models under `topic_model`, along with the DTM used to build the model, the corpus of origin (overview or manuals), the word and topic distributions results from that model, it's evaluation measures, and vectors of words and topics that allow us humans to get a feel of the model, along with some key words.
```{r LDA fit, cache = TRUE, eval = TRUE}
initial_time <- Sys.time()
topic_numbers <- seq(from = 4, to = 8, by = 2)

@@

  ) %>%
  mutate(Origin     = rep(c("catalogues", "manuals"), length(topic_numbers)),         # should be 50
         `Topic ID` = paste(Origin, n_topic, sep = "_"),

@@

         #Fit Model
         Model  = pmap(.l = list(n_topic, DTM), .f = my_LDA, control = my_control), #my_control
